Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
RQ2
paragraph on agents

@@

Agent-based architectures \cite{lin2024swiftsage} \cite{ghafarollahi2024sciagents}
Reasoning and Acting (ReAct)

>>>>

\paragraph{Agents}. An important step forward in using LLMs are agent-based architectures \cite{lin2024swiftsage} \cite{ghafarollahi2024sciagents}. They allow the LLM to act as an intelligent being capable of planning a solution of a complex task, while resorting to external resources on the way to acquire in-context the knowledge it does not have from pre-training. The retrieved information, results of invoking tools, such as calculators, and of interactions with the environment are appended to the prompt (or, in a more advanced scenario, to the summarized memory). Optionally, a reflexion step (explicit reasoning on all the accumulated information) is added before allowing further generation of the final response.

@@
